COG-ED Manuscript

### 2021-12-08 06_Paper/COG-ED/Manuscript.Rmd
prepare results for report

  data_nfc$subject[which(data_nfc$subject == "E12K08")] <- "E12K08_neu"

@@

  # simple slopes analysis -----------------------------------------------------
  library(interactions)

@@

  names(summary(m1_h2b))
  m1_h2b.fixef <- summary(m1_h2b)$coefficients
  m1_h2b.ranef <- as.data.frame(summary(m1_h2b)$varcor)
  write.csv2(te.norm.fixef, file = "S4_te.norm.fixef.csv")
  write.csv2(te.norm.ranef, file = "S4_te.norm.ranef.csv")

  # TODO: Corinna go on here :) 
    # -> get results for reporting
    # -> get means for plotting, plot results (if requested)
    # -> write methods
    # -> write results

  # TODO: it would be easy to integrate NFC as level 2 predictor into the analysis
    # to identify the personality influence on sv
    # it goes in the same direction as hypothesis 3a, but would hold some more information
    # a corresponding hypothesis could be
    # "SVs decline stronger with increasing load level for individuals with low compared to high NFC scores" 
    # What do you think?

@@

intraclass correlation "icc_h2b"
table withterm/parameter - Beta - SE - p-value - random effects (SD)
huxtable?

>>>>

  # prepare temporary nfc-data frame for loop to feed into

    data_nfc <- rbind(data_nfc, data.frame(subject = data_quest$subject[setindex[i]],
                                           nfc = sum(nfc)))
  }
  data_nfc$subject[which(data_nfc$subject == "E12K08")] <- "E12K08_neu"

@@

  # simple slopes analysis -----------------------------------------------------

  library(interactions)

@@

  # FIXME: Do not print all charts

  # prepare results for reporting ----------------------------------------------

  names(summary(m1_h2b))
  m1_h2b.fixef <- summary(m1_h2b)$coefficients
  m1_h2b.ranef <- as.data.frame(summary(m1_h2b)$varcor)

  h2b_result.table <- as.data.frame(cbind(row.names(m1_h2b.fixef), 
                                          m1_h2b.fixef[,c(1, 2, 5)]))
  h2b_result.table$ranef.sd <- NA
  h2b_result.table$ranef.sd[c(1,2)] <- m1_h2b.ranef$sdcor[c(1,2)]
  colnames(h2b_result.table)[1] <- "Parameter"
  colnames(h2b_result.table)[2] <- "Beta"
  colnames(h2b_result.table)[3] <- "SE"
  colnames(h2b_result.table)[4] <- "p-Value"
  colnames(h2b_result.table)[5] <- "Random Effects (SD)"

  row.names(h2b_result.table) <- NULL
  h2b_result.table$Parameter[1:8] <- c("Intercept", "N-Back Level", "NFC", "D-Prime", "RT", "Correct", "Post-Correct", "Level x NFC")
  # FIXME: display control variables? Spelling lower/upper case

  h2b_result.table[2:5] <- lapply(h2b_result.table[2:5], as.numeric)

  h2b_result.table[c(2,3,5)] <- round(h2b_result.table[c(2,3,5)], digits = 2)
  h2b_result.table[4] <- round(h2b_result.table[4], digits = 3)

  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.001)] <- 
    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.001)],"*")
  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.01)] <- 
    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.01)],"*")
  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.05)] <- 
    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.05)],"*")

  # FIXME: display of p = 0.000,  no display of NA

  apa_table(h2b_result.table,
            caption = "Subjective values decline with increasing n-back level, even after controlling for declining task 
            performance (d’ and reaction time), correct and postcorrect trials.",
            note = "")

  # TODO: Corinna go on here :) 
    # -> prepare tables: MLM results + huxtable
    # -> write methods
    # -> write results

  # TODO: 
    # -> check whether we want to include an additional hypothesis
    # "SVs decline stronger with increasing load level for individuals with low compared to high NFC scores" 
    # What do you think?

@@

(`r apa_table(h2b_result.table)`)

intraclass correlation "icc_h2b"

huxtable?
